Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2016-02-19 cordillera-cycle.tex
Add references to Matthias' reconstructions.

      The location of the modelled ice-dispersal centres is potentially biased
      by the present day ice volumes contained in the ETOPO1 basal topography
      data. Although a~recent reconstruction of the thickness of the western
      Canadian glaciers south of 60{\degree}N \citep{Clarke.etal.2013} shows
      that the
      most problematic part of the model domain in this respect is by far
      that of the Wrangell and Saint Elias mountains, where ice thicknesses
      of up to 1200\,m have been measured by a low-frequency radar
      \citep{Rignot.etal.2013}. In this area, located over the USA-Canada
      border just north of 60{\degree}N, temperate ice, glacier surging
      dynamics and deep subglacial depressions in the icefield interior pose
      a~fundamental challenge to the reconstruction basal topography for the
      entire ice cap \citep{Rignot.etal.2013}. Although this causes our
      simulations to overestimate ice surface topography in this region, we
      are not aware of bed topography reconstructions.
      However, this drawback seem to have
      little effect on modelled Cordilleran ice sheet dynamics. In fact, the
      Wrangell and Saint Elias mountains, heavily glacierized at present,
      host an ice cap for the entire length of both simulations, but that
      ice cap does not appear to be a~major feed to the Cordilleran ice
      sheet (Fig.~\ref{fig:hr_geom_duration}, WSEM). With this
      exception of the Wrangell and Saint Elias mountains ice field,
      present-day ice volumes are small relative to the ice volumes
      concerned in our study.

@@

@@

>>>>

      The location of the modelled ice-dispersal centres is potentially biased
      by the present day ice volumes contained in the ETOPO1 basal topography
      data. The most problematic part of the model domain in this respect is
      that of the Wrangell and Saint Elias mountains, where ice thicknesses
      of up to 1200\,m have been measured by a low-frequency radar
      \citep{Rignot.etal.2013}. In this area, located over the USA-Canada
      border just north of 60{\degree}N, temperate ice, glacier surging
      dynamics and deep subglacial depressions in the icefield interior pose
      a~fundamental challenge to the reconstruction basal topography for the
      entire ice cap \citep{Rignot.etal.2013}. Recent ice thickness
      reconstructions available for all glaciers around the globe
      \citep{Huss.Farinotti.2012}, for Canadian glaciers south of 60{\degree}N
      \citep{Clarke.etal.2013}, and for Alaska tidewater glaciers
      \citep{McNabb.etal.2015} have not been implemented in our simulations.
      However, this drawback seem to have
      little effect on modelled Cordilleran ice sheet dynamics. In fact, the
      Wrangell and Saint Elias mountains, heavily glacierized at present,
      host an ice cap for the entire length of both simulations, but that
      ice cap does not appear to be a~major feed to the Cordilleran ice
      sheet (Fig.~\ref{fig:hr_geom_duration}, WSEM). With this
      exception of the Wrangell and Saint Elias mountains ice field,
      present-day ice volumes are small relative to the ice volumes
      concerned in our study.

@@

\bibitem[{Huss and Farinotti(2012)}]{Huss.Farinotti.2012}
Huss, M. and Farinotti, D.: Distributed ice thickness and volume of all glaciers around the globe, J. Geophys. Res. Earth Surf., 117, F04\,010,
doi:\href{http://dx.doi.org/10.1029/2012JF002523}{10.1029/2012JF002523}, 2012.

@@

\bibitem[{McNabb et~al.(2015)McNabb, Hock, and Huss}]{McNabb.etal.2015}
McNabb, R.~W., Hock, R., and Huss, M.: Variations in Alaska tidewater glacier frontal ablation, 1985--2013, J. Geophys. Res. Earth Surf., 120, 120--136,
doi:\href{http://dx.doi.org/10.1002/2014JF003276}{10.1002/2014JF003276}, 2015.
